Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")

@@

>>>>

origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
```
## Wrangling
```{r Predictors}
## Use 80% of data for training
train <- origin %>% 
    slice(1:40)

## Use 20% for testing
test <- origin %>% 
    slice(41:50)

# Visualize linear relationship between predictors (lat, lon, state) and predicted value

@@

## Models 
```{r Linear Regression}
## Create the recipe
rec <- origin %>% 
    recipe(value ~ lat + lon + state) 
rec

model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

wf1 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model)
wf1

res <- fit(wf1, data = train)

## Check performance on the complete training data
res %>% 
    extract_fit_engine() %>% 
    summary()

## Check performance using cross-validation
folds <- vfold_cv(train, v = 10)
folds
res <- fit_resamples(wf1, resamples = folds)
res %>% 
    collect_metrics()
```
